---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




```{r}
queue_step(arrivals = as.numeric(df2$ArrivalTime[c(136,137,138,139)]), service = df2$TotalServerTime[c(136,137,138,139)], due = as.numeric(df2$DueTime[c(136,137,138,139)]), servers = 1)

df2[c(136,137,138,139),]


date1 = read.xlsx(xlsxFile="Assist Projections - All Games, modified inflow, with player tracking - Predicted Ramp.xlsx", sheet="Queue - HR ", startRow = 2, detectDates = TRUE, cols = c(1))
time1 = read.xlsx(xlsxFile="Assist Projections - All Games, modified inflow, with player tracking - Predicted Ramp.xlsx", startRow = 2, sheet="Queue - HR ", cols = c(3))
ArrivalTime = as.POSIXct(paste(date1$Date, "00:00:00 EST")) + 86400*(time1$Time)
game1 = read.xlsx(xlsxFile="Assist Projections - All Games, modified inflow, with player tracking - Predicted Ramp.xlsx", sheet="Queue - HR ", startRow = 2, cols = seq(7,21))
game1[is.na.data.frame(game1)] = 0
game1$`PT.Danish.HRs-72`=game1$PT.Danish.HRs*(5/7)
game1$`PT.Danish.HRs-24`=game1$PT.Danish.HRs*(2/7)
game1$`PT.Champ.HRs-72`=game1$PT.Champ.HRs*(5/12)
game1$`PT.Champ.HRs-24`=game1$PT.Champ.HRs*(7/12)
df = data.frame(ArrivalTime, game1[c(seq(1,13),seq(16,19))])
df2 = df %>% gather(Type, TotalServerTime, -ArrivalTime) %>% filter(TotalServerTime!=0)
df2$ArrivalTime = as.POSIXct(df2$ArrivalTime , format = "%Y-%m-%d %h:%m:%s" , tz = "CDT") 
df2 = df2[ order(df2$ArrivalTime),]
cols = colnames(df)[2:18]
df2$TurnAround = ifelse(df2$Type %in% cols[c(1,4,7)],43200,ifelse(df2$Type %in% cols[c(2,5,8,10,11,12,13,15,17)],86400,ifelse(df2$Type %in% cols[c(3,6,9,14,16)],518400,0)))
df2$DueTime = df2$ArrivalTime + df2$TurnAround
df2$AveTime = ifelse(df2$Type %in% cols[c(1,2,3)],110/60,ifelse(df2$Type %in% cols[c(4,5,6)],10/60,ifelse(df2$Type %in% cols[c(7,8,9)],20/60,ifelse(df2$Type %in% cols[c(10,11,12,13)],130/60,ifelse(df2$Type %in% cols[c(14,15,16,17)],120/60,0)))))
df2$NumJobs = ceiling(df2$TotalServerTime/df2$AveTime)
df2$ServerTime = df2$TotalServerTime/df2$NumJobs
df2 = df2[rep(row.names(df2), df2$NumJobs),]
#df2$TotalTime = 3600*queue_step(arrivals = as.numeric(df2$ArrivalTime), service = df2$ServerTime, due = as.numeric(df2$DueTime), servers = 11)$departures_df$system_time
df2$TotalTime = 3600*finish_times(arrivals = as.numeric(df2$ArrivalTime), service = df2$ServerTime, due = as.numeric(df2$DueTime), servers = 11)$system_time
df2$ServerNum = queue_step(arrivals = as.numeric(df2$ArrivalTime), service = df2$ServerTime, due = as.numeric(df2$DueTime), servers = 11)$departures_df$server
df2$FinishTime = df2$ArrivalTime + df2$TotalTime
df2$StartTime = df2$FinishTime - 3600*df2$ServerTime
df2$OnTime = df2$DueTime > df2$FinishTime

mean(df2$OnTime[seq(1,500)])

as.numeric(dff$ArrivalTime)[1]-1501563500

dff = df2[1:150000,]
dff$TotalTime = finish_times(arrivals = as.numeric(dff$ArrivalTime)-1501563500, service = dff$ServerTime*3600, due = as.numeric(dff$DueTime)-1501563500, servers = 250)$system_time
dff$FinishTime = dff$ArrivalTime + dff$TotalTime
dff$StartTime = dff$FinishTime - 3600*dff$ServerTime
dff$OnTime = dff$DueTime > dff$FinishTime
dff$BeforeLastHour = dff$DueTime > dff$FinishTime + 3600

mean(dff$OnTime[seq(1,150000)])
mean(dff$BeforeLastHour[seq(1,150000)])


arrivals = c(100,102,104,104,106,135,137,144,145,146,146)
service = c(7,3,4,7,10,4,6,4,4,4,4)
due = c(200,300,175,150,200,400,100,200,300,400,500)
servers = 2

arrivals = c(144,145,146,146,147)
service = c(4,4,4,4,4)
due = c(200,200,200,500,600)
servers = 2

arrivals = c(100,104,107,107)
service = c(6,.5,4,10)
due = c(200,150,100,55)
servers = 1

finish_times(arrivals, service, due, servers)



finish_times = function(arrivals, service, due, servers){
  n = length(arrivals)
  output = vector("numeric", (n+1) * 2 - 1)
  queue_times = vector("numeric", servers)
  h=0
i=1
due2 = due
serv2 = service
arr = arrivals
arr2 = arrivals
for (j in 1:length(arr2)){
  if (j%%100 == 0){
    print(j)
  }
    queue = which.min(queue_times)
    if (queue_times[queue] < arrivals[1]){
      i=which.min(due[arrivals[1]>=arrivals])
      queue_times[queue] = max(c(arrivals[i], queue_times[queue])) + service[i]
      output[which(arr2==arrivals[i])[i]] = queue_times[queue]
      output[which(arr2==arrivals[i])[i]+n] = queue + 1
      arr2[which(arr2==arrivals[i])[i]]=queue_times[queue]
    } else{
       i = which.min(due[arrivals<=queue_times[queue]])
       queue_times[queue] = queue_times[queue] + service[i]
       h = which(arrivals[i] == arr2)[which.min(due2[which(arrivals[i] == arr2)])]
      arr2[h] = queue_times[queue]
      output[h] = queue_times[queue]
      output[h+n] = queue + 1
    }
    arrivals=arr[which(arr == arr2)]
    due=due2[which(arr == arr2)]
    service=serv2[which(arr == arr2)]
}
data = data.frame("arrivals"=arr,"service"=serv2,"departures"=output[1:length(arr)])
data$waiting = data$departures - data$service-data$arrivals
data$system_time = data$service + data$waiting
  return(data)
}


sum(dff$StartTime < dff$ArrivalTime)


for(i in 1:n){
    queue = which.min(queue_times)
    queue_times[queue] = max(c(arrivals[i], queue_times[queue])) + service[i]
    
    if (queue_times[queue] < arrivals[i]){
      queue_times[queue] = max(c(arrivals[i], queue_times[queue])) + service[i]
    } else{
      arrivals[i:binsearch(function(y) arrivals[y]-queue_times[queue], range=c(1,           length(arrivals)))$where[1]][which.min(due[i:binsearch(function(y) arrivals[y]-queue_times[queue], range=c(1,length(arrivals)))$where[1]])]
      
      
    }
    
    output[i] = queue_times[queue]
    output[i + n] = queue + 1
  }






x <- c(4, 8, 15, 16, 23, 42)
binsearch(function(y) x[y]-24, range=c(1, length(x)))$where[1]

finish_times(arrivals, service, due, servers)


queue_step(arrivals = arrivals, service = service, due=due, servers = servers)

queue_pass(arrivals = arrivals, service = service, servers = servers)

queue(arrivals = arrivals, service = service, due=due, servers = servers)

df2[245:255,]

queue(arrivals = as.numeric(df2$ArrivalTime), service = df2$ServerTime, due = as.numeric(df2$DueTime), servers = 11)


ordstatement <- is.unsorted(arrivals)

  # Order arrivals and service according to time

  if(ordstatement){
    ord <- order(arrivals, method = "radix")
    due <- due[ord]
    arrivals <- arrivals[ord]
    service <- service[ord]
  }




qloop_numeric(arrivals, service, servers)


queue_lengths(due, 0, c(105,108,112,119,129))


arrivals <- cumsum(rexp(10))
service <- rexp(10)
queue_obj <- queue_step(arrivals, service, rev(arrivals))

depart(queue_obj)
queue_obj$departures_df$departures


queue_step(arrivals = as.numeric(df2$ArrivalTime), service = df2$ServerTime, due = as.numeric(df2$DueTime), servers = 100)$departures_df[572:582,]

queue_step(arrivals = as.numeric(df2$ArrivalTime[572:582]), service = df2$ServerTime[572:582], due = as.numeric(df2$DueTime[572:582]), servers = 1)$departures_df

toy = df2[,]

toy$AveTime = ifelse(df2$Type %in% cols[c(1,2,3)],110/60,ifelse(df2$Type %in% cols[c(4,5,6)],10/60,ifelse(df2$Type %in% cols[c(7,8,9)],20/60,ifelse(df2$Type %in% cols[c(10,11,12,13)],130/60,ifelse(df2$Type %in% cols[c(14,15,16,17)],120/60,0)))))

toy$NumJobs = ceiling(toy$TotalServerTime/toy$AveTime)
toy$ServerTime = toy$TotalServerTime/toy$NumJobs
toy = toy[rep(row.names(toy), toy$NumJobs),]

toy

```




queue_pass <- function(arrivals, service, servers){
  UseMethod("queue_pass", servers)
}


queue_pass.numeric <- function(arrivals, service, servers){
  stopifnot((servers%%1 == 0) & (servers > 0))
  stopifnot(length(servers) == 1)
  output <- qloop_numeric(arrivals, service, n_servers = servers)
  return(output)
}


queue_pass.server.stepfun <- function(arrivals, service, servers){

  x = c(servers$x, Inf)
  y = c(servers$y, 1)

  if(length(x) != 2){
    if( any(max(service) >= diff(x))){
      warning("Service times may span multiple server epochs. Results may not be 100% accurate")
    }
  }

  output <- qloop_qq(arrivals, service, x, y)
  return(output)
}


queue_pass.server.list <- function(arrivals, service, servers){
  Number_of_queues <- length(servers)

  queue_times <- mapply(next_function, servers, rep(0, Number_of_queues))
  output <- rep(NA, length(arrivals))
  queue_vector <- rep(NA,length(arrivals))

  for(i in 1:length(arrivals)){
    test_queue_times <- pmax.int(queue_times, arrivals[i])
    new_queue_times <- mapply(next_function, servers, test_queue_times)
    queue <- which.min(new_queue_times)

    queue_times[queue] <- new_queue_times[queue] + service[i]
    output[i] <- queue_times[queue]
    queue_vector[i] <- queue
  }
  return(c(output, queue_vector, NA))
}



qloop_numeric <- function(times, service, n_servers) {
    .Call('queuecomputer_qloop_numeric', PACKAGE = 'queuecomputer', times, service, n_servers)
}

qloop_qq <- function(times, service, x, y) {
    .Call('queuecomputer_qloop_qq', PACKAGE = 'queuecomputer', times, service, x, y)
}



queue_lengths <- function(arrivals, service = 0, departures){

  value <- NULL
  key <- NULL
  state <- NULL
  times <- NULL
  queuelength <- NULL

  if(length(service) == 1){
    stopifnot(service == 0)
    check_queueinput(arrivals, service = departures)
  } else {
    check_queueinput(arrivals, service, departures)
  }

  queuedata <- tidyr::gather(
    data.frame(
      input = due,
      output = departures - service
    ),
    factor_key = TRUE
  )

  state_df <- data.frame(
    key = as.factor(c("input", "output")),
    state = c(1, -1)
  )

  queuedata <- suppressMessages(
    dplyr::left_join(queuedata, state_df)
  )

  # queuedata <- queuedata %>% arrange(value, key) %>% mutate(
  #   QueueLength = cumsum(state),
  #   time = value
  # )

  ord <- order(queuedata$value, queuedata$key, method = "radix")

  queuedata <- queuedata[ord, ]

  queuedata <- dplyr::mutate(
    queuedata,
    queuelength = cumsum(state),
    times = value
  )

  queuedata <- dplyr::select(queuedata, times, queuelength)

  zerodata <- data.frame(
    times = 0, queuelength = 0
  )

  queuedata <- dplyr::bind_rows(zerodata, queuedata)

  return(queuedata)

}